### 2016-05-14 sec5_baseline.tex
Introduction Almost Done
Need resolve comments

\section{Temporal Replication and Mining}
\label{sec:trm_solution}
The idea of \emph{Temporal Replication and Mining} (TRM)
is to group temporally closed snapshots together, such that patterns can be
mined on each group of the snapshot. In order to achieve the \emph{completeness}
and \emph{soundness} during partitioning, we allow replication of
snapshots among groups. The TRM is described in Algorithm~\ref{algo:trm_overview}.

%%The straightforward strategy of parallelizing the second stage is to vertically partition the trajectories based on snapshots. 
%A simple but effective method
%is to group neighborhood snapshots into a partition, such that every possible pattern can be mined within some of the partitions. In order to achieve the \emph{completeness},
%some of the snapshots need to be replicated on multiple executors.
%We call this method the \emph{Temporal Replication and Mining} approach. 
%The algorithm is presented as in Algorithm~\ref{algo:trm_overview}.

\begin{algorithm}
\caption{Temporal Replication and Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State {---Map Phase---}
\label{code:trm-map-start}
\ForAll{$\langle t, S_t \rangle$}
	\ForAll{$i \in 1...(K-1)*G+K$}
		\State emit a $\langle t-i, S_t \rangle$ pair
	\EndFor 
\EndFor
\label{code:trm-map-end}
\State {---Partition and Shuffle Phase---}
\label{code:trm-par-start}
\ForAll{$\langle t, S \rangle$ pair} 
\State group-by $t$, emit a $\langle t, Par_t\rangle$,
\State  where $Par_t = \{S_t, S_{t+1}, .. S_{t+(\lfloor \frac{K}{L} \rfloor -1)*G+K+L}\} $
\EndFor
\label{code:trm-par-end}
\State {---Reduce Phase---}
\label{code:trm-red-start}
\ForAll{$\langle t,Par_t \rangle$}
\State lineSweepMining($Par_t$)
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}

As shown in Algorithm~\ref{algo:trm_overview}, the TRM algorithm takes
three steps. First, in the map phase, each snapshot is keyed with its timestamp (lines~\ref{code:trm-map-start}-\ref{code:trm-map-end}). Second, in the partition phase, every snapshot is grouped with its next $(\lfloor \frac{K}{L} \rfloor -1)*G+K+L$ snapshots to form a partition (lines~\ref{code:trm-par-start}-\ref{code:trm-par-end}). We will shortly discuss how the group size is determined. Third, in the reduce phase, a lineSweepMining method is invoked to mine GCMP within each partition (lines~\ref{code:trm-red-start}-\ref{code:trm-red-end}). 
It is easy to see that this method replicates a snapshots at most $(\lfloor \frac{K}{L} \rfloor -1)*G+K+L$ times.

\subsubsection{Temporal Replication Partition}
The size of replication is critical for the performance of TRM algorithm.
If the size of replication is too large, the shuffle cost as well as the reduce cost would be high. 
On the contrary, if the size of replication is too small, the \emph{completeness} and \emph{soundness}
properties cannot be satisfied. In the Algorithm~\ref{algo:trm_overview}, 
the partition size is chosen as $(\lfloor \frac{K}{L} \rfloor -1)*G+K+L$. As stated in the following
theorem, such a partition method is sound and complete.
\begin{theorem}[Soundness and Completeness of Replication]
\label{thm:replication_partition}
Let $\mathbb{P}$ be as follows: for each snapshot $S_t$, create a partition $Par_t = \{S_t, ...,S_{t+(\lfloor \frac{K}{L}-1\rfloor *G+K + L )}\}$. Then $\mathbb{P}$ is sound and complete.
\end{theorem}
\begin{proof}
The soundness of partition is trivial.
Given a valid pattern $P$, let $T' \subseteq P.T$ be the subsequence of $P.T$ which conforms to $K,L,G$ with the smallest size. Note that there could be many qualified $T'$s.  
Let the $i^{th}$ local-consecutive part of $T'$ be $l_i$ and let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can be written as $\Sigma_i (l_i + g_i)$. 
Since $T'$ conforms to $K,L,G$, then $K+L \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. Therefore, $\Sigma_i(l_i+g_i) \leq \lfloor \frac{K}{L}-1\rfloor *G+K+L$. Thus ensuring each $Par_t$ to be of that size would capture at least one of the $T'$s, therefore the pattern $P$ would valid in $Par_t$. This proves the completeness of the partitioning method.
\end{proof}

\subsubsection{Line Sweep Mining}
After partition, each task in the reduce phase processes a partition $Par_i$, which contains
$\lfloor \frac{K}{L}-1 \rfloor *G+K+L$ snapshots starting from snapshot $S_i$. With such a 
partition method, we observe that within $Par_i$, only the 
patterns whose object sets are contained in the first snapshot are necessary to be reported.
Therefore, we design a simple \emph{line-sweep mining}(LSM) method for discover
GCMPs. The algorithm works as in Algorithm~\ref{algo:line-sweep}.

@@

The algorithm scans the snapshots in a partition in the sequential order.During the scan it
maintains a candidate set $C$ which could potentially be a valid pattern (line~\ref{code:ls-can-set}).
The algorithm starts by inserting clusters at $S_1$ to $C$ (lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
Subsequently, in each iteration, clusters in $C$ are joined with clusters at $S_i$ to generate
a new set of patterns $N$(lines~\ref{code:ls-join}). Any valid new patterns are inserted back to $C$
and any invalid patterns are discarded(lines~\ref{code:ls-add} and~\ref{code:ls-remove}).

@@

\begin{example}
We illustrate the process of \emph{Trajectory Replication and Mining} in Figure~\ref{fig:trm_process} using $M=2, K=2, L = 2, G=2$. In (a), snapshots are clustered and these snapshots are the input to the TRM. Then, we compute the size 
for each partition, which equals to $\lfloor \frac{K}{L}-1 \rfloor *G+K+L = 4$. Therefore, in (b), every four snapshots
are grouped into a partition. Then a line sweep method is performed in (c) for partition 1. Each
$C_i$ refers to the candidate set  when the algorithm sweeps each snapshot. Initially, $C_1$ contains
patterns whose object set is in $S_1$. When scanning the other snapshots, patterns in $C_1$ grow
their timestamps. At $S_3$, since the timestamps of $\{o_5,o_6\}$ is $\{1,2\}$ which is neither
a qualified pattern nor matches $G$ constraint, thus this candidate is removed from $C_3$. When line
sweep finishes, only $\{o_3,o_4\}$ is the qualified pattern and is outputted.
\end{example}

The TRM approach though achieves good parallelism, 
it requires to replicate the data multiple times. 
Specifically, each snapshots are copied $\lfloor \frac{K}{L}-1 \rfloor *G+K+L$ times. 
In the cases of \emph{swarm}, \emph{group} and \emph{platoon}, $G$ is as large as $|T|$. 
Handling those cases is equivalent to replicate the entire snapshots to each partition, 
which surrenders the benefit of parallelism.

>>>>

\section{Temporal Replication and Mining}
\label{sec:trm_solution}
The idea of \emph{Temporal Replication and Mining} (TRM)
is to group temporally contiguous snapshots together, s.t. patterns can be
mined from each group of snapshots. In order to achieve the \emph{completeness}
and \emph{soundness} during partitioning, we allow replication of
snapshots among groups. The TRM is outlined in Algorithm~\ref{algo:trm_overview}.

\begin{algorithm}
\caption{Temporal Replication and Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State {---Map Phase---}
\label{code:trm-map-start}
\ForAll{$\langle t, S_t \rangle$}
	\ForAll{$i \in 1...(K-1)*G+K$}
		\State emit a $\langle t-i, S_t \rangle$ pair
	\EndFor 
\EndFor
\label{code:trm-map-end}
\State {---Partition and Shuffle Phase---}
\label{code:trm-par-start}
\ForAll{$\langle t, S \rangle$ pair} 
\State group-by $t$, emit a $\langle t, Par_t\rangle$,
\State  where $Par_t = \{S_t, S_{t+1}, .. S_{t+(\lceil \frac{K}{L} \rceil -1)*G+2K}\} $
\EndFor
\label{code:trm-par-end}
\State {---Reduce Phase---}
\label{code:trm-red-start}
\ForAll{$\langle t,Par_t \rangle$}
\State lineSweepMining($Par_t$)
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}

As shown in Algorithm~\ref{algo:trm_overview}, the TRM algorithm contains
three steps. First, in the map phase, each snapshot is keyed 
with its timestamp (lines~\ref{code:trm-map-start}-\ref{code:trm-map-end}). 
Second, in the partition phase, every snapshot is grouped with its next 
$(\lceil \frac{K}{L} \rceil -1)*G+2K$ snapshots to form a partition (lines~\ref{code:trm-par-start}-\ref{code:trm-par-end}). We will shortly discuss how the group size is derived. 
Third, in the reduce phase, a lineSweepMining method is invoked 
to mine GCMP within each partition (lines~\ref{code:trm-red-start}-\ref{code:trm-red-end}). 
It is easy to see that this method replicates a snapshots 
at most $(\lceil \frac{K}{L} \rceil -1)*G+2K$ times.

\subsubsection{Temporal Replication Partition}
The size of replication is critical for the performance of TRM algorithm.
If the size of replication is too large, the shuffle cost as well as the reduce cost would be high. 
On the contrary, if the size of replication is too small, the \emph{completeness} and \emph{soundness}
properties cannot be satisfied. In the Algorithm~\ref{algo:trm_overview}, 
the partition size is chosen as $(\lceil \frac{K}{L} \rceil -1)*G+2K$. As stated in the following
theorem, such a partition method is sound and complete.
\begin{theorem}[Soundness and Completeness of Replication]
\label{thm:replication_partition}
Let $\mathbb{P}$ be as follows: for each snapshot $S_t$, create a partition $Par_t = \{S_t, ...,S_{t+(\lceil \frac{K}{L} \rceil - 1) *G+2K}\}$. Then $\mathbb{P}$ is sound and complete.
\end{theorem}
\begin{proof}
The soundness of partition can be observed from the fact that each partition represents partial trajectories with consecutive snapshots, therefore patterns in a partition can be directly mapped back to original trajectories.
Given a valid pattern $P$, let $T' \subseteq P.T$ be the subsequence of $P.T$ which conforms to $K,L,G$ with the smallest size. Note that there could be many qualified $T'$s.  
Let the $i^{th}$ local-consecutive part of $T'$ be $l_i$ and let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can be written as $\Sigma_i (l_i + g_i)$. 
Since $T'$ conforms to $K,L,G$, then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. Therefore, $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. Thus ensuring each $Par_t$ to be of that size would capture at least one of the $T'$s, therefore the pattern $P$ would be valid in $Par_t$. This proves the completeness of the partitioning method.
\end{proof}

\subsubsection{Line Sweep Mining}
After partition, each task in the reduce phase processes a partition $Par_i$, which contains
$(\lceil \frac{K}{L} \rceil -1) *G+2K$ snapshots starting from snapshot $S_i$. With such a 
partition method, we observe that within $Par_i$, only the 
patterns whose object sets are contained in the first snapshot are necessary to be reported.
Therefore, we design a simple \emph{line-sweep mining}(LSM) method for discover
GCMPs. The algorithm works as in Algorithm~\ref{algo:line-sweep}.

@@

The algorithm scans the snapshots in a partition in sequential order. During the scan, it
maintains a candidate set $C$ which could potentially be a valid pattern (line~\ref{code:ls-can-set}).
The algorithm starts by inserting clusters at $S_1$ to $C$ (lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
Subsequently, in each iteration, clusters in $C$ are joined with clusters at $S_i$ to generate
a new set of patterns $N$(lines~\ref{code:ls-join}). Any valid new patterns are inserted back to $C$
and any invalid patterns are discarded(lines~\ref{code:ls-add} and~\ref{code:ls-remove}).

@@

\begin{example}
We illustrate the process of TRM in Figure~\ref{fig:trm_process} using $M=2, K=2, L = 2, G=2$. In (a), snapshots are clustered and these snapshots are the input to the TRM. Then, we compute the size 
for each partition, which equals to $(\lceil \frac{K}{L} \rceil-1) *G+2K = 4$. Therefore, in (b), every four snapshots
are grouped into a partition. Then a line sweep method is performed in (c) for partition 1. Each
$C_i$ refers to the candidate set  when the algorithm sweeps each snapshot. Initially, $C_1$ contains
patterns whose object set is in $S_1$. When scanning the other snapshots, patterns in $C_1$ grow
their timestamps. At $S_3$, since the timestamps of $\{o_5,o_6\}$ is $\{1\}$ which is neither
a qualified pattern nor matches $G$ constraint, thus this candidate is removed from $C_3$. When line
sweep finishes, only $\{o_3,o_4\}$ is the qualified pattern and is outputted.
\end{example}

The TRM approach though achieves good parallelism, 
it requires to replicate the data multiple times. 
Specifically, each snapshots are copied $(\lceil \frac{K}{L} \rceil -1) *G+2K$ times. 
In the cases of \emph{swarm}, \emph{group} and \emph{platoon}, $G$ is as large as $|T|$. 
Handling those cases is equivalent to replicate the entire snapshots to each partition, 
which surrenders the benefit of parallelism.

### 2016-05-14 sec6_spm.tex
Introduction Almost Done
Need resolve comments

\section{Star Partition and Mining}
\label{sec:spm_solution}
In order to develop a method that achieves good parallelism under any pattern parameters, 
we propose the \emph{Star Partition and Mining} (SPM) method. In SPM,
we first design a novel object-based partition method named \emph{star partition}. 
Then, we design an \emph{Apriori}-like 
method to mine GCMP patterns out of each partition.
The overview of the SPM method is presented in Algorithm~\ref{algo:spm_overview}.
As shown, the SPM method takes three phases. 
In the map phase, objects from the same cluster forms object-object pairs. 
The object-object pairs are then paired up with the timestamp of 
the snapshot to form a 3-uple(lines~\ref{code:spm-map-start}-\ref{code:spm-map-end}). 
In the partition phase, 3-uples with the same leading object form a \emph{star} which will be explained shortly 
(lines~\ref{code:spm-shuffle-start}-\ref{code:spm-shuffle-end}).
Lastly in the reduce phase, patterns are mined from each star structure (lines~\ref{code:spm-reduce-start}-\ref{code:spm-reduce-end}).

@@

\subsubsection{Star Partition}
The intuition of star partition is that, if two objects are part of
the same pattern, then at some snapshots, they must belong to the same 
cluster. Therefore, we may link objects that belong to the same cluster
at some snapshots to form a \emph{connection graph}. Objects that are
not connected surely do not belong to a pattern. We may further
partition the connection graph so that mining proper patterns can be
done in parallel. We define the \emph{connection graph} and \emph{star}
as follows:
\begin{definition}[Connection Graph and Star]
A connection graph is an undirected graph $G=(V:E)$, where 
each $v \in V$ represents an object. An edge $e(s,t)= ET \in E$ 
contains all the timestamps at which $s,t$ are in the same cluster,
i.e., $\forall t \in ET, C_t(s) = C_t(t)$. 
A star of a vertex $s$, denoted as $Sr_s$, is the set of incidental edges on $s$ whose
another ending vertex is greater than $s$. I.e, $\forall e(s,t) \in Sr_s$, $s < t$. We name $s$
as the \emph{central vertex} of $Sr_s$.
\end{definition}

@@

Based on the above theorem, we can mine GCMP from each partition independently.
It is notable that, in star partition, original data is replicated for $O(\mathbb{O})$ times
as each object may be sent to $O(\mathbb{O})$ partitions. Since this complexity is free
from pattern parameters, the star partition is more scalable than the temporal replication.
In later sections, we will describe several engineering level optimization to further reduce the amount of replicated data.

\subsubsection{Apriori Mining}
In the mining phase, we need to find the patterns within each star. 
To systematically discover the patterns, we design the \emph{Apriori Mining} method which
is similar to the technique in frequent item mining literature. During the algorithm, we call a candidate pattern $R$-pattern if the size of its object set is $R$. 
Our algorithm runs in iterations. During each iteration $R$, we try to generate all $(R+1)$-patterns. In iteration $1$, the $2$-pattern is the edges in $Sr_s$. In particular,
for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. During each iteration, 
we generate $(R+1)$-patterns by joining $R$-patterns with $2$-patterns. Specifically,
the join between $p_1=(O_1, T_1)$ and $p_2=(O_2, T_2)$ would generate a new pattern $p_3=(O_1 \cup O_2, T_1 \cap T_2)$. Notice that in $Sr_s$, each $R$-pattern consists of the object $s$, thus the join will grow a $R$-pattern at most to a $(R+1)$-pattern.
Our mining algorithm stops where no further patterns are generated. The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.

>>>>

\section{Star Partition and Mining}
\label{sec:spm_solution}
In order to develop a method that achieves good parallelism 
under any pattern parameters, we propose 
the \emph{Star Partition and Mining} (SPM) method. In SPM,
we first design a novel object-based partition method named \emph{star partition}. 
Then, we adapt an \emph{Apriori}-like 
method to mine GCMP patterns out of each partition.
The overview of the SPM method is presented in Algorithm~\ref{algo:spm_overview}.
As shown, the SPM method takes three phases. 
In the map phase, objects from the same cluster forms object-object pairs. 
The object-object pairs are then paired up with the timestamp of 
the snapshot to form a triplet(lines~\ref{code:spm-map-start}-\ref{code:spm-map-end}). 
In the partition phase, triplets with the same leading object form a \emph{star} which will be explained shortly 
(lines~\ref{code:spm-shuffle-start}-\ref{code:spm-shuffle-end}).
Lastly in the reduce phase, patterns are mined from each star structure (lines~\ref{code:spm-reduce-start}-\ref{code:spm-reduce-end}).

@@

\subsubsection{Star Partition}
The intuition of star partition is that, if two objects are part 
of the same pattern, they must belong to the same cluster at 
some snapshots. Therefore, we may link objects that belong to the same cluster to form a \emph{connection graph}. Objects that are
not connected surely fail to form a pattern. We may then
partition the connection graph based on vertex connectivity
s.t. mining GCMPs can be done in parallel. We define the \emph{connection graph} and \emph{star}
as follows:
\begin{definition}[Connection Graph and Star]
A connection graph is an undirected graph $G=(V:E)$, where 
each $v \in V$ represents an object. An edge $e(s,t)= ET \in E$ 
contains all the timestamps at which $s,t$ are in the same cluster,
i.e., $\forall t \in ET, C_t(s) = C_t(t)$. 
A star of a vertex $s$, denoted as $Sr_s$, is the set of incidental edges on $s$ whose
another ending vertex is greater than $s$. I.e, $\forall e(s,t) \in Sr_s$, $s < t$. We name $s$
as the \emph{central vertex} of $Sr_s$.
\end{definition}

@@

Based on the above theorem, we can mine GCMP from each partition independently.
It is notable that, in star partition, original data is replicated for $O(|\mathbb{O}|)$ times
as each object may be sent to $O(|\mathbb{O}|)$ partitions. Since this complexity is free
from pattern parameters, the star partition is more scalable than the temporal replication.
In later sections, we will describe several engineering level optimization to further reduce the amount of replicated data.

\subsubsection{Apriori Mining}
In the mining phase, we need to find the patterns within each star. 
To systematically discover the patterns, we design the \emph{Apriori Mining} method which
is similar to the technique in frequent item mining literature. During the algorithm, we call a candidate pattern $R$-pattern if the size of its object set is $R$. 
Our algorithm runs in iterations. During each iteration $R$, we try to generate all $(R+1)$-patterns. In iteration $1$, the $2$-pattern is the edges in $Sr_s$. In particular,
for each $e(s,v)=ET$, pattern $p=(\{s,v\}, ET)$ is formed. During each iteration, 
we generate $(R+1)$-patterns by joining $R$-patterns with $2$-patterns. Specifically,
the join between $p_1=(O_1:T_1)$ and $p_2=(O_2:T_2)$ would generate a new pattern $p_3=(O_1 \cup O_2:T_1 \cap T_2)$. Notice that in $Sr_s$, each $R$-pattern consists of the object $s$, thus the join will grow a $R$-pattern at most to a $(R+1)$-pattern.
Our mining algorithm stops where no further patterns are generated. The algorithm is illustrated as in Algorithm~\ref{algo:apriori_mining}.

### 2016-05-14 sec7_optimization.tex
Further edits on Sec1 and sec4
Introduction Almost Done
Need resolve comments

\subsection{Candidate Pruning via Temporal Monotonicity}
During the apriori phase, we repeatedly join candidate patterns in different levels to generate a larger set
of a patterns. We observe that traditional monotonic property of Apriori algorithms \textbf{does not}
hold in GCMP mining. That is given two candidate $P_1, P_2$, if $P_1.O \subset P_2.O$ and $P_1$ is not 
a valid pattern, then $P_2$ may or may not be a valid pattern. However, we notice that
we may form another monotonic property based on the \emph{candidate sequence} such that
the Apriori algorithm could still benefit.

@@

\begin{example}
We use Figure~\ref{fig:star_partition} (c) to demonstrate the candidate pruning. As shown, at the initial stage, $\{3,6\}\{1,4\}$ is pruned, since $\{1,4\}$ is not a candidate sequence. By temporal monotonicity, candidates containing objects $\{3,6\}$ can all be pruned. Therefore, we are able to directly prune $\{3,4,6\}$, $\{3,5,6\}$ and $\{3,4,5,6\}$.
\end{example}
%
%With the help of the \emph{Monotonic Property}, the number of new candidates in each level is greatly reduced. We verify this in the experiment session as well.
\subsection{Load Balancing}

@@

>>>>

\subsection{Candidate Pruning}
\subsubsection{Temporal monotonicity}
During the apriori phase, we repeatedly join candidate patterns in different levels to generate a larger set
of a patterns. We observe that traditional monotonic property of Apriori algorithms \textbf{does not}
hold in GCMP mining. That is given two candidate $P_1, P_2$, if $P_1.O \subset P_2.O$ and $P_1$ is not 
a valid pattern, then $P_2$ may or may not be a valid pattern. However, we notice that
we may form another monotonic property based on the \emph{candidate sequence} such that
the Apriori algorithm could still benefit.

@@

\subsubsection{Forward closure checking}

\begin{example}
We use Figure~\ref{fig:star_partition} (c) to demonstrate the candidate pruning. As shown, at the initial stage, $\{3,6:1,4\}$ is pruned, since $\{1,4\}$ is not a candidate sequence. By temporal monotonicity, candidates containing objects $\{3,6\}$ can all be pruned. Therefore, we are able to directly prune $\{3,4,6\}$, $\{3,5,6\}$ and $\{3,4,5,6\}$.
\end{example}
%
%With the help of the \emph{Monotonic Property}, the number of new candidates in each level is greatly reduced. We verify this in the experiment session as well.
\subsection{Load Balancing}

@@

\subsection{Handling Overlapping Clusters}
